### 2019-04-01 Introduction.tex
sections 1-3 fixes

% A key research question in multi-label text classification is how to model and leverage the dependencies among labels.
Naively, one could predict each label independently without considering label dependencies. This approach is called Binary Relevance \cite{DBLP:journals/pr/BoutellLSB04,tsoumakas2007multi}, and is widely used  due to its simplicity, but it often does not deliver good performance.  Intuitively, knowing some labels---such as \texttt{sport} and \texttt{football}---should make it easier to predict \texttt{2018 world cup} and then \texttt{Russia}.  There are several methods that try to capture label dependencies by building a joint probability estimation over all labels  $p(\mathbf{y}=(y_1,y_2,...,y_L)|x)$ \cite{ghamrawi2005collective,read2009classifier,DBLP:conf/icml/DembczynskiCH10,li2016conditional}. 
% \kechen{put BR before the introduction of dependency? because there is nothing about dependency by using BR} 
The most popular approach, Probabilistic Classifier Chain (PCC) \cite{DBLP:conf/icml/DembczynskiCH10} learns and predicts labels one-by-one in a predefined fixed order: for each label, it uses one classifier to estimate the probability of that label given all previous labels predictions, $p(y_l|y_1,...,y_{l-1},x)$. PCC's well known drawback is that errors in early predictions tend to propagate to subsequent predictions, and can become massive when the total number of label candidates $L$ is large. \kechen{clarify PCC define set probability while RNN define sequence probability? check our email to Krzysztof}
% since PCC has to make a decision regarding each label candidate.

@@

Both PCC and RNN rely heavily on label orders in training and prediction. But in multi-label data, the labels are given as sets, not necessarily with natural order - thus various ways of arranging sets as sequences have been explored:  ordered alphabetically,  by frequency, based on a label hierarchy, or according to some label ranking algorithm \cite{liu2015optimality}. The experimental results show that which order to choose can have a significant impact on learning and prediction \cite{vinyals2015order,DBLP:conf/nips/NamMKF17,DBLP:conf/aaai/ChenCYW18}. In the above example, starting label predictions sequence with \texttt{Russia}, while correct, would make the other predictions very difficult.

@@

\section{Mapping Sequences to Sets} 
In this section, we formulate how existing works map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order\kechen{, where $T$ is the maximum number of labels in a document}; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each timestep $t$ puts different weights on different words (features) and thus effectively attends on a list of important words. \kechen{The context vector $c_t$ is computed as the weighted average over the dense representation of the words.} The selected words $c_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(c_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})
\label{eq:standard_rnn}
\end{align}
\kechen{where $N$ is the total number of samples in the corpus and $n$ represents the $n$-th sample.} \newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

>>>>

% A key research question in multi-label text classification is how to model and leverage the dependencies among labels.
Naively, one could predict each label independently without considering label dependencies. This approach is called Binary Relevance \cite{DBLP:journals/pr/BoutellLSB04,tsoumakas2007multi}, and is widely used  due to its simplicity, but it often does not deliver good performance.  Intuitively, knowing some labels---such as \texttt{sport} and \texttt{football}---should make it easier to predict \texttt{2018 world cup} and then \texttt{Russia}.  There are several methods that try to capture label dependencies by building a joint probability estimation over all labels  $p(\mathbf{y}=(y_1,y_2,...,y_L)|x)$ \cite{ghamrawi2005collective,read2009classifier,DBLP:conf/icml/DembczynskiCH10,li2016conditional}. 
% \kechen{put BR before the introduction of dependency? because there is nothing about dependency by using BR} 
The most popular approach, Probabilistic Classifier Chain (PCC) \cite{DBLP:conf/icml/DembczynskiCH10} learns and predicts labels one-by-one in a predefined fixed order: for each label, it uses one classifier to estimate the probability of that label given all previous labels predictions, $p(y_l|y_1,...,y_{l-1},x)$. PCC's well known drawback is that errors in early predictions tend to propagate to subsequent predictions, and can become massive when the total number of label candidates $L$ is large. 
% since PCC has to make a decision regarding each label candidate.

@@

Both PCC and RNN rely heavily on label orders in training and prediction. In multi-label data, the labels are given as sets, not necessarily with natural order.  RNN define a sequence probability (dynamically) while PCC define set probability (statically, sets are built in a predefined order). Various ways of arranging sets as sequences have been explored:  ordered alphabetically,  by frequency, based on a label hierarchy, or according to some label ranking algorithm \cite{liu2015optimality}. The experimental results show that which order to choose can have a significant impact on learning and prediction \cite{vinyals2015order,DBLP:conf/nips/NamMKF17,DBLP:conf/aaai/ChenCYW18}. In the above example, starting label predictions sequence with \texttt{Russia}, while correct, would make the other predictions very difficult.

@@

\section{Mapping Sequences to Sets} 
In this section, we formulate how existing works map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order, where $T$ is the maximum number of labels in a document; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each timestep $t$ puts different weights on different words (features) and thus effectively attends on a list of important words. The context vector of selected words $c_t$ is computed as the weighted average over the dense representation of the words. The context $c_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(c_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})
\label{eq:standard_rnn}
\end{align}
where $N$ is the total number of documents in the corpus. \newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

### 2019-04-01 Model.tex
sections 1-3 fixes

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$. In standard maximum likelihood training, one wishes to maximize the likelihood of given label sets, namely, $\prod_{n=1}^N p(\mathbf{y}^{(n)}|x^{(n)})=\prod_{n=1}^N \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})$, or equivalently, 
\begin{align}
\maximize \sum_{n=1}^N \log \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})
\label{eq:right_obj}
\end{align}
  % Having this clearly defined set probability is critical for our formulation as it naturally leads to our training and prediction methods.

@@

This training objective (\ref{eq:right_obj}) looks similarly to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

@@

    % \underline{function Beam\_Search\_for\_Given\_Set} $(\mathbf{y},m)$\;
    \Input{Instance $x$ \\
    Subset of labels considered $G\subset \mathcal{L}$\\
    Boolean flag $ALL$: 1 if sequences must contain all $G$ labels; 0 if partial sequences are allowed }
    \Output{A list of top sequences and the associated probabilities} 
    Let $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ be the top $K$ sequences  found so far. Initially, all $K$ sequences are empty. $\oplus$ means concatenation. \\
    % Let $C$ be the set of candidate sequences, initially empty.\\
    \While {true}{
     // Step 1: Generate Candidate Sequences from each existing sequence $s_k \in K$ and all possible new labels $l \in G\setminus s_k$:\\
    Expand all non-stopped sequences:\\
     $C = \{ \mathbf{s}_k\oplus l | l\in G,  l \notin s_k, STOP \notin s_k \}$\\
Include stopped sequences:\\
    $C = C \cup \{ \mathbf{s}_k | STOP \in s_k \}$\\
    Terminate non-stopped sequences:\\
    \If{$ALL==0$}{
    % Add $\mathbf{s}_k\oplus STOP$ to $C$  }
    %
    $C =C \cup \{ \mathbf{s}_k\oplus STOP | STOP \notin s_k \}$
    }

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up $|\mathbf{y}|!$  sequence probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set.  Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

@@

    % Initialize model parameters\\
    \ForEach {epoch, batch}{
        % \ForEach {batch }{
            \ForEach{$(x^{n},\mathbf{y}^{n})$ in the batch}{
                Get top $K$ sequences :\\
		    	$\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}, p(\mathbf{s}^n_{1}|x^n),...,p(\mathbf{s}^n_{K}|x^n)\}$=  \hspace{4ex}=Beam\_Search($(x^{n},\mathbf{y}^{n}, ALL=1$)\\
                }
            Update model parameters by maximizing $\sum\limits_{(x^{n},\mathbf{y}^{n}) \in \text{batch}} \log \sum\limits_{\mathbf{s}\in\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}\}} p(\mathbf{s}|x^{n})$
        % }
    }
    \caption{Training method for set-RNN}
    \label{alg:train_beam}
\end{algorithm}

@@

>>>>

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$.   
  % \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. }
  To be precise, our label ``permutations'' $\pi$ are sequences that allow repetitions (i.e. $(y_1,y_2,y_3,y_1,...)$), up to a maximum length. So the set probability sums over all such permutations, and both training and prediction candidate sets are generated this way. In practice, we dont think this detail makes any difference, as sequences with repeated labels are extremely rare; however in theory we want to allow the attention context to focus on any recent labels it chooses to (repeated if necessary).

  In standard maximum likelihood training, one wishes to maximize the likelihood of given label sets, namely, $\prod_{n=1}^N p(\mathbf{y}^{(n)}|x^{(n)})=\prod_{n=1}^N \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})$, or equivalently, 
\begin{align}
\maximize \sum_{n=1}^N \log \sum_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})} p(\mathbf{s}|x^{(n)})
\label{eq:right_obj}
\end{align}
  % Having this clearly defined set probability is critical for our formulation as it naturally leads to our training and prediction methods.

@@

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. 
Using Jensen’s inequality, one can show that the total probability mass in Eq. 3 will be less than or equal to the true amount of probability mass in Eq. 1. In this sense, previous work is optimizing a bound on the log-likelihood, while we are optimizing it directly.

If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

@@

    % \underline{function Beam\_Search\_for\_Given\_Set} $(\mathbf{y},m)$\;
    \Input{Instance $x$ \\
    Subset of labels considered $G\subset \mathcal{L}$\\
    Boolean flag $ALL$: 1 if sequences must contain all $G$ labels; 0 if partial sequences are allowed }
    \Output{A list of top sequences and the associated probabilities} 
    Let $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ be the top $K$ sequences  found so far. Initially, all $K$ sequences are empty. $\oplus$ means concatenation. \\
    % Let $C$ be the set of candidate sequences, initially empty.\\
    \While {true}{
     // Step 1: Generate Candidate Sequences from each existing sequence $s_k \in K$ and all possible new labels $l \in G\setminus s_k$:\\
    Expand all non-stopped sequences:\\
     % $C = \{ \mathbf{s}_k\oplus l | l\in G,  l \notin s_k, STOP \notin s_k \}$\\
     $C = \{ \mathbf{s}_k\oplus l | l\in G, STOP \notin s_k \}$\\    
Include stopped sequences:\\
    $C = C \cup \{ \mathbf{s}_k | STOP \in s_k \}$\\
    Terminate non-stopped sequences:\\
    \If{$ALL==0$}{
    % Add $\mathbf{s}_k\oplus STOP$ to $C$  }
    %
    $C =C \cup \{ \mathbf{s}_k\oplus STOP | STOP \notin s_k \}$
    }

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up sequence (permutation) probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set. Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

@@

    % Initialize model parameters\\
    \ForEach {batch}{
        % \ForEach {batch }{
            \ForEach{$(x^{n},\mathbf{y}^{n})$ in the batch}{
                Get top $K$ sequences :\\
		    	$\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}, p(\mathbf{s}^n_{1}|x^n),...,p(\mathbf{s}^n_{K}|x^n)\}$=  \hspace{4ex}=Beam\_Search($(x^{n},\mathbf{y}^{n}, ALL=1$)\\
                }
            Update model parameters by maximizing $\sum\limits_{(x^{n},\mathbf{y}^{n}) \in \text{batch}} \log \sum\limits_{\mathbf{s}\in\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}\}} p(\mathbf{s}|x^{n})$
        % }
    }
    \caption{Training method for set-RNN}
    \label{alg:train_beam}
\end{algorithm}

@@

Both our method and the comparison sate-of-the-art RNN takes more time than a vanilla-RNN, by a factor of $K$, because there are $K$ permutations for each datapoint. Our proposed method is slower than the RNN baseline by a factor of 1.5 (approximatively) because each epoch requires one more forward pass.
